High Mass Resolution Time of Flight Mass Spectrometer for Measuring Products in Heterogeneous Catalysis in Highly Sensitive Microreactors

### 2012-04-22 paper.tex
Incorporated corrections from Ib except changing system overview figure

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis optimization and development of analytic equipment is important both to minimize the cost of equipment but also to be able to experimentally study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}. Such a platform has been developed to test and characterize model catalysts in our department\cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements. The QMS, however, suffers from a low mass resolution ($m/\Delta m\gtrsim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a low mass range (typically $\sim$\mbox{100--200}\,amu) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored. GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and are in general difficult to use as mass spectrometers due to the difficult interpretation of measurements on complex mixtures. Furthermore, GCs only sample a very small part of the converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity. As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($m/\Delta m>1000$), fast acquisition of full mass spectra ($>$1\,Hz) and high sensitivity making them suitable for characterization of very small amounts of catalyst, i.e. model systems, and a mass range only limited by the detector. With a standard available microchannel plate (MCP) used as detector a mass range of \mbox{0--5000}\,amu can be obtained.

@@

The microreactor is heated by joule heating of a 100\,nm platinum strip (on top of a 3\,nm Ti adhesion layer) evaporated through a shadow mask on the backside of the chip . The heating element is contacted by two pogo pins which are connected to a power supply. Two additional contacts are placed on the chip facilitating a 4 wire measurement of the resistance of the heating element. The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip. In the current configuration temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached.

@@

The prize of the TOF including ionization gauge, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is estimated to USD80000 which is comparable to a high quality QMS which is prized at approximately USD85000.

In Figure~\ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C) is shown. Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and hydroxyl (OH) which have a mass difference of 23\,milli-amu.
\begin{figure}
 \includegraphics[width=16cm]{untreated_data.png}%
 \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C). Subfigures show three different regions of the spectrum. From the first subfigure in the lower panel a delay between the acquisition trigger and the noise signal from the rise of the high voltage pulser of approximately 150\,ns can be seen. This is due to delays in cables and the repeller pulser. In the center subfigure the extremely good separation between individual masses is shown. It is evident that 1\,amu corresponds to approximately 850\,ns difference in flight time in our system in the mass regime around 1\,amu. In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milli-amu mass difference).\label{fig:untreated_data}}%
\end{figure}

@@

As a demonstration of the system performance ammonia oxidation on 1\,\% geometrical coverage Pt thin film was performed. The ability to resolve OH and NH$_3$ which is separated by 23\,milli-amu was demonstrated. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signals. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where the mass range is limited to $\sim500$\,amu and can be applied to the study of small amounts of catalysts.

%\section{Acknowledgements}

>>>>

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite, \ref, and \label commands
\section{Introduction}
In heterogeneous catalysis optimization and development of analytic equipment is important both to minimize the cost of equipment but also to be able to experimentally study complicated systems. As a platform for testing heterogeneous catalysts microfabricated reactors or microreactors have been found suitable due to both high surface-to-volume ratio, fast temperature response and minimization of thermal and concentration gradients\cite{Jensen2001,Jaehnisch2004}. Such a platform has been developed to test and characterize model catalysts in our department\cite{Henriksen2009}. However, a suitable reactor platform is only part of the task; reactant and product detection and characterization is essential to determine catalyst performance. Typically, quadrupole mass spectrometers (QMSs) are used in low pressure regimes to analyze gas composition while gas chromatographs (GCs) are used for high pressure measurements. The QMS, however, suffers from a low mass resolution ($m/\Delta m\gtrsim m$ up to $m\sim200$) which makes analysis of complicated spectra difficult and cumbersome. The QMS is additionally subject to a mass dependent transmission (typically $\propto m^{-1}$ ) limiting general use. Furthermore, QMSs are typically operated by logging a single (or a few) masses as a function of time to increase time resolution. This is at the expense of acquisition of full mass spectra during the experiment limiting operation by potentially losing interesting features in other masses not monitored. GCs have inherently low time resolution which make them unsuitable for fast time response measurements as in the case of microreactors and are in general difficult to use as mass spectrometers due to the difficult interpretation of measurements on complex mixtures. Furthermore, GCs only sample a very small part of the converted gas making them unsuitable for small amounts of reactant and product gases due to the low sensitivity. As an alternative to GCs or QMSs time of flight mass spectrometers (TOF-MS) offer both high mass resolution ($m/\Delta m>1000$), fast acquisition of full mass spectra ($>$1\,Hz) and high sensitivity making them suitable for characterization of very small amounts of catalyst, i.e. model systems, and a mass range only limited by the detector. With a standard available microchannel plate (MCP) used as detector a mass range of \mbox{0--5000}\,amu can be obtained.

@@

The microreactor is heated by joule heating of a 100\,nm platinum strip (on top of a 3\,nm Ti adhesion layer) evaporated through a shadow mask on the backside of the chip . The heating element is contacted by two pogo pins which are connected to a power supply. Two additional contacts are placed on the chip facilitating a 4 wire measurement of the resistance of the heating element. The heating strip can in this way be used as a resistance temperature detector (RTD) to determine the temperature of the chip. Currently, temperatures from room temperature to approximately 450\,$^{\circ}$C can be reached due to apparatus limitations. The high temperature limit is expected to be $\sim600$\,$^{\circ}$C where the pyrex lid used for sealing the reactor will melt.

@@

The prize of the TOF including ionization gauge, 8" 4-way cross, control electronics, data acquisition hardware and MCP detector is comparable to the prize of a high quality QMS with electronics making the TOF-MS a serious alternative to a QMS.

In Figure~\ref{fig:untreated_data} an example spectrum of ammonia oxidation (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C) is shown. Here the high resolution of the TOF-MS is demonstrated by resolving ammonia (NH$_3$) and hydroxyl (OH) which have a mass difference of 23\,milli-amu.
\begin{figure}
 \includegraphics[width=16cm]{untreated_data.png}%
 \caption{Raw data acquired from the TOF-MS during NH$_3$ oxidation by O$_2$ (NH$_3$:O$_2$ 4:3, 195\,$^{\circ}$C). Subfigures show three different regions of the spectrum. From the first subfigure in the lower panel a delay between the acquisition trigger and the noise signal from the rise of the high voltage pulser of approximately 150\,ns can be seen. This is due to delays in cables and the repeller pulser. In the center subfigure the extremely good separation between individual masses is shown. It is evident that 1\,amu corresponds to approximately 1.4\,$\mu$s difference in flight time in our system in the mass regime around 1\,amu. In the last subfigure a zoom of the ammonia and hydroxyl peaks region shows separation between OH and NH$_3$ as well as O and NH$_2$  (23\,milli-amu mass difference).\label{fig:untreated_data}}%
\end{figure}

@@

As a demonstration of the system performance ammonia oxidation on 1\,\% geometrical coverage Pt thin film was performed. The ability to resolve OH and NH$_3$ which is separated by 23\,milli-amu was demonstrated. The resolution of reactants and products enables simple and straightforward quantification of the ammonia and water signals. This greatly simplifies the analysis compared to conventional QMSs used for gas analysis. The setup is furthermore superior to conventional QMSs where only a limited mass resolution at high masses can be obtained and can be applied to the study of small amounts of catalysts.

\section{Acknowledgements}
This work was carried out as part of the Catalysis for Sustainable Energy initiative, which is funded by the Danish Ministry of Science, Technology and Innovation. The Center for Individual Nanoparticle Functionality is funded by the Danish National Research Foundation.
